Direction-aware functional class scoring enrichment analysis of Infinium DNA methylation data

### 2024-02-22 manuscript/manuscript.Rmd
affiliation

<strong>
Mark Ziemann<sup>1,2*</sup>,
Mandhri Abeysooriya<sup>2,3</sup>,
Anusuiya Bora<sup>1,2</sup>,
Séverine Lamon<sup>3</sup>,
Mary Sravya Kasu<sup>1</sup>,
Mitchell W. Norris<sup>1</sup>,
Yen Ting Wong<sup>4,5</sup>,
Jeffrey M. Craig<sup>4,5</sup>
</strong>

>>>>

<strong>
Mark Ziemann<sup>1,2*</sup>,
Mandhri Abeysooriya<sup>2,3</sup>,
Anusuiya Bora<sup>1,2</sup>,
Séverine Lamon<sup>3</sup>,
Mary Sravya Kasu<sup>2</sup>,
Mitchell W. Norris<sup>2</sup>,
Yen Ting Wong<sup>4,5</sup>,
Jeffrey M. Craig<sup>4,5</sup>
</strong>
